% tex file for regression

% tex file for regression
\par \indent A simple and straightforward way to model the voxel time courses
is to preform linear regression. Initially, we just used the convoluted predicted
hemodyamic response (HR) using all the conditions together and each of 
conditions individually. After realizing that the HRs themselves didn't explain
enough of the BOLD ratio, we attempted to add features in order to reduce/ explain
the noise we observed. Additional features that we examined included a 
linear drift, a small set the fourier series, and a few principle components.

Linear regression stems from the assumption that there exists a linear relationship 
between an observation's response,$y_i$ with it's features $x_i$ (a vector who's 
first element is $1$ and the rest are the values the observation $i$'s features are) 
in the following manner:

\begin{equation}
y_i = x_i^T \beta + \epsilon_i
\label{eq:one_1d_lin_reg}
\end{equation}

where $\epsilon_i \sim N(0, \sigma^2)$. Moveover we assume all observations $i$, the $\epsilon_i$ are independent and that the true $\beta$ value is the same. Equation \ref{eq:one_1d_lin_reg} can be expressed in matrix form in the following manner (\ref{eq:mat_lin_reg}):

\begin{equation}
Y = X\beta + \epsilon
\label{eq:mat_lin_reg}
\end{equation}

This relationship leads to creating a $X$ feature matrix, which presents each distinct feature
as a column and sees each observation get a single row to represent it's values.
Normality of the errors, more specifically 
$\epsilon \sim N(0,\sigma^2 I)$, is a not trivial assumption, so we will need to check 
the validity of such a assumption (discussed in the \textit{"Normality Assumptions"} 
section). As might be expected, we do not know the true value of $\beta$ and as such
need to estimate, using matrix algebra we get a closed from solution:

\begin{equation}
\hat{\beta} =(X^T X)^{-1} X^T y
\end{equation}

This equation does require $(X^T X)$ to be invertible, but even when it is not, we
can use the psuedo inverse, represented  $(X^T X)^{-}$ to get a non-unique value
for $\hat{\beta}$.
\par To consider the strength of the effects of these predictors, we looked 
at t-tests of the corresponding estimated coefficients for each voxel, as 
discussed under \textit{"Hypothesis Testing"}. The validity of these t-tests and 
their corresponding "p-values" is largely dependent on how good our assumptions 
of linearity and normally-distributed errors are. 

\subsubsection{More about potential features:}
\par Other than the basic HR feature/features, and a column of $1$s in our feature matrix
which accounts for a ``intercept'' term/ non-zero average value, we experimented with 
include a few features for the first principle components of a of time $\times$ time 
matrix and the first few functions of the Fourier series.  As noted above these 
additional features helped account for the noise in the observed BOLD ratio 
fluxuation.

\vspace{2mm}
\textbf{Principle Components}
\vspace{2mm}
\par This matrix use to obtain the principle components was the correlation between 
each individual voxel time course with other voxel's time course ($A^TA$ where 
$A$ is a voxel $time$ time matrix). It should be noted that we only use the voxel 
time courses for voxels that we knew were in the brain. ***Add Jane's Stuff about 
why we'd need to use the first 6 pcs***

\vspace{2mm}
\textbf{Fourier Series}
\vspace{2mm}
\par We included 4 - 6 features related to the first few functions of the Fourier series.
The full fourier series is represent as the following:

\begin{equation}
f(x) = \frac{1}{2} \cdot a_0 + \sum_{n=1}^{\infty} a_n \cdot cos(n x) + \sum_{n=1}^{\infty} b_n \cdot  sin(n x)
\end{equation}

but since strength of Fourier series strength comes from orthogonality of the range, 
and we are looking for a function of the range $(0, \text{num of TR})$, we change it to:

\begin{equation}
f(x) = \frac{1}{2} \cdot a_0 + \sum_{n=1}^{\infty} a_n \cdot cos(\frac{n}{\text{num of TR}} x) + \sum_{n=1}^{\infty} b_n \cdot sin(\frac{n}{\text{num of TR}} x)
\end{equation}

We used $ + \sum_{n=1}^{2} a_n \cdot cos(\frac{n}{\text{num of TR}} x) + 
\sum_{n=1}^{2} b_n \cdot sin(\frac{n}{\text{num of TR}} x)$ to be 4 features to try 
to get a low order sinusoidal fluxucations. The idea behind including fourier series 
would be they would be less likely to over fit/take the response from the hemodyamic 
response than principle components and that could account for larger period level 
fluctuation that might exist.

